\documentclass[a4paper,9pt]{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}

% Define custom colors
\usepackage{xcolor}
\definecolor{mycolor}{RGB}{0, 51, 102}

% Define custom font size and style for section titles
\titleformat{\section}{\large\bfseries\color{mycolor}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries\color{mycolor}}{}{0em}{}
\titleformat{\subsubsection}[runin]{\bfseries\color{mycolor}}{}{0em}{}

\hypersetup{
    colorlinks=true,
    linkcolor=mycolor,
    urlcolor=mycolor,
}

\begin{document}

\begin{center}
    \textbf{\Huge Rafiqul Alam Chisty} \\[0.5em]
    \href{mailto:racs.chisty@gmail.com}{racs.chisty@gmail.com} | +4917685923008 \\[0.5em]
    \href{https://linkedin.com/in/rafiqul-chisty}{LinkedIn} | \href{https://leetcode.com/u/racs/}{LeetCode}
\end{center}

\section*{Summary}
Experienced Quality Assurance Specialist with 9+ years in computer security products and mobile financial services. Proven track record in leading manual and automated testing processes for global financial companies such as Kona, Alipay, and bKash. Adept at collaborating with cross-functional teams to brainstorm solutions, optimize processes, and deliver high-quality software. Skilled in a wide range of testing tools and methodologies, including Selenium, Appium, JMeter, and Agile development.

\section*{Skills}
\begin{multicols}{2}
    \begin{itemize}
        \item Programming Languages: C, Java, Groovy, Python, Node.js (beginner)
        \item Databases: MySQL, Oracle
        \item Web Servers: Apache Tomcat, Glassfish, Wildfly
        \item Build Tools: Maven, Gradle
        \item Bug Trackers: Redmine, JIRA
        \item Source Control: Git
        \item Development Processes: Scrum, Agile
        \item Automation Tools: Selenium, Appium, Spock Framework, JMeter, RESTAssured, Robot Framework
        \item Testing Tools: Postman, Testrail
        \item Log Monitoring: Logmx, WinSSH
    \end{itemize}
\end{multicols}

\section*{Experience}

\subsection*{Quality Assurance Specialist (Mid-Senior) | Nord Security}
\textit{Oct 2022 - Present (1 year 11 months)}
\begin{itemize}
    \item Led the execution of manual and automated tests, reducing software defects by 30\% and streamlining the overall testing process.
    \item Conducted exploratory tests, identifying and resolving critical discrepancies, improving software reliability.
    \item Created and maintained 200+ test cases in X-ray using Gherkin syntax, enhancing test coverage and accuracy.
    \item Collaborated with stakeholders to perform requirement analysis, identifying and resolving 10 potential grey areas, leading to a clearer project scope.
    \item Managed daily testing tasks, ensuring on-time delivery of all testing milestones.
    \item Executed cross-browser testing on web portals, ensuring 100\% compatibility across major browsers.
    \item Diagnosed and resolved system issues by analyzing logs, reducing troubleshooting time by 20\%.
    \item Optimized the release process in collaboration with cross-functional teams, reducing release cycle time by 25\% while maintaining high-quality standards.
    \item Contributed to a 95\% defect detection rate by performing daily manual regression and functional tests.
    \item Validated API correctness using Postman, identifying and resolving 50+ API issues, ensuring robust backend functionality.
    \item Proposed and implemented process improvements, increasing testing efficiency by 15\%.
    \item Developed and maintained automated regression tests, improving test coverage by 30\%.
\end{itemize}

\subsection*{Assistant Lead Engineer | bKash Limited}
\textit{Sep 2019 - May 2022 (2 years 9 months)}
\begin{itemize}
    \item Led functional testing efforts using Postman, improving API reliability and performance.
    \item Documented and managed test cases in Testrail, ensuring comprehensive test coverage for multiple projects.
    \item Automated API testing using the Spock Framework, increasing test execution speed by 20\%.
    \item Conducted server-side and client-side application validation, identifying and resolving critical issues, enhancing overall system stability.
    \item Automated Android application testing using Java and Appium, reducing manual testing time by 30\%.
    \item Collaborated with offshore partner teams to seamlessly integrate testing processes, ensuring consistent quality across projects.
    \item Reported project status to stakeholders, ensuring transparency and timely updates on project progress.
\end{itemize}

\subsection*{Software QA Engineer Level-2 | Kona SL}
\textit{Jan 2017 - Aug 2019 (2 years 8 months)}
\begin{itemize}
    \item Developed and supervised the "Decepticon" mobile app automation tool using Java and Appium Framework, significantly improving testing efficiency.
    \item Versioned and managed the Decepticon project in Git, ensuring proper version control and collaboration.
    \item Wrote automation test scripts in Java/Groovy utilizing the Spock Framework, enhancing test automation capabilities.
    \item Performed regression and performance testing using Postman and JMeter, identifying performance bottlenecks and ensuring smooth system operation.
    \item Automated Android application testing using Java and Appium, streamlining the testing process and reducing errors.
\end{itemize}

\subsection*{SQA Engineer Level-1 | Kona SL}
\textit{Jun 2015 - Jan 2017 (1 year 8 months)}
\begin{itemize}
    \item Wrote and maintained automation test scripts in Java/Groovy, increasing test coverage and reducing manual testing efforts.
    \item Executed functional testing using Postman, ensuring the stability and functionality of APIs.
    \item Documented test cases and bugs, improving the tracking and resolution of issues.
    \item Automated Android application testing using Java and Appium, improving testing efficiency and accuracy.
\end{itemize}

\subsection*{Junior Quality Assurance Engineer | Kona SL}
\textit{May 2014 - Jun 2015 (1 year 2 months)}
\begin{itemize}
    \item Conducted functional testing using Postman, ensuring the reliability and performance of APIs.
    \item Documented test cases and identified issues from server logs, leading to faster bug resolution and improved system performance.
    \item Performed server-side and client-side application validation, ensuring end-to-end system functionality.
\end{itemize}

\section*{Education}
\textbf{BSc in Computer Engineering | University of Dhaka} \\
\textit{Jan 2010 - Dec 2013} \\
Studied Computer Science and Engineering.

\section*{Licenses \& Certifications}
\begin{itemize}
    \item Certified Secure Software Lifecycle Professional - Skillsoft
\end{itemize}

\section*{Additional Skills}
\begin{itemize}
    \item Python (Programming Language), JavaScript, Automated Software Testing, Agile Methodologies, Start-ups, Integration Testing, Functional Testing, Programming, Test Cases, Regression Testing
\end{itemize}

\end{document}
